The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-03-13 analysis/paper/paper.qmd
Update subject and document stopwords functions

#head_text(emu_theses$text)

# clean text 
emu_theses$text_clean <- emu_theses$text %>%
  clean_basic() %>%
  str_remove_all(find_meta_stopwords(emu_theses) )

```

@@

# Add latitude and longitude information to theses data frame
emu_theses <- geocode_thesis_locations(emu_theses, location = NULL)

# Show thesis locations on world map
visualize_thesis_locations(emu_theses)
```

@@

stop_words_custom <- emu_theses %>% 
  unnest_tokens(output = word, input = title) %>%   ### add words from the title
  select(word) %>% 
  rbind(., data.frame(word = c("preface", "foreword", "introduction", "conclusion", "thesis", 
                               "source", "author"))) %>% 
  # rbind(., data.frame(word = c("city", "urban", "urbanism"))) %>% 
  rbind(., data.frame(word = c("hab", "km")))

emu_theses_words <- emu_theses %>%
  mutate(author = paste(first_name, last_name)) %>% 
  select(author, title, text, -c(graduation_year, first_name, last_name)) %>% 
  unnest_tokens(output = word, input = text) %>%   # remove punctuation, convert to lowercase, seperate all words
  anti_join(stop_words, by = "word") %>%  # remove stop words
  anti_join(stop_words_custom, by = "word")
```

>>>>

emu_theses$text_clean <- emu_theses$text |>
  clean_basic() |>
  str_remove_all(find_meta_stopwords(emu_theses)) |> 
  str_remove_all(subject_stopwords()) |> 
  str_remove_all(document_stopwords())
```

@@

# Geocode thesis locations
emu_theses <- emu_theses %>%
  geocode(location, method = 'osm', lat = latitude , long = longitude)

# Show thesis locations on world map
world <- map_data("world")
ggplot() +
  geom_map(
    data = world, map = world,
    aes(long, lat, map_id = region),
    color = "black", fill = "lightgray", size = 0.1
  ) +
  geom_point(data = emu_theses, aes(longitude, latitude), color = "red") +
  coord_fixed() +
  theme_void()
```

@@

urbanism_stopwords <- urbanism_stopwords() 
thesis_stopwords <- thesis_stopwords()

emu_theses_words <- emu_theses |> 
  select(title, text_clean) |> 
  unnest_tokens(output = word, input = text_clean) |>   # remove punctuation, convert to lowercase, seperate all words
  anti_join(stop_words, by = "word") |> 
  anti_join(urbanism_stopwords, by = "word") |> 
  anti_join(thesis_stopwords, by = "word")
```
